Non-word repetition in Yélî Dnye

### 2020-12-18 manuscript.Rmd
make all legends fit on fig1

myplot = ggplot(data = pl, aes(x = Age, y = Score, color = Language))+
  geom_point(aes(size = n, shape = Length))+
  geom_line(aes(linetype=Length)) + 
  theme(text = element_text(size = 16),
    legend.position="none", axis.text.x=element_text(colour="black")) +
  scale_color_manual(values = palette)+
  theme_bw()+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  scale_x_continuous(name = "Age (years) ", limits = c(4,12), breaks = c(4,8,12))+

>>>>

myplot = ggplot(data = pl, aes(x = Age, y = Score, color = Language))+
  geom_point(aes(size = n, shape = Length))+
  geom_line(aes(linetype=Length)) + 
  theme(text = element_text(size = 16),
    legend.position="none", axis.text.x=element_text(colour="black")) +
  scale_color_manual(values = palette)+
  theme_bw()+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), legend.key.height = unit(5, "mm"))+
  scale_x_continuous(name = "Age (years) ", limits = c(4,12), breaks = c(4,8,12))+
